19Q1

### 2019-03-08 19Q1.Rmd
concat CCLE, CTRP, and GDSC AUC data--Needs editing

```{r}
library(ggpubr)
library(ggrepel)
library(ggsignif)
library(kableExtra)
library(reshape2)
library(tidyverse)
theme_set(theme_light())
```

@@

18Q3, Gene expression data (Reads Per Kilobase of transcript, per Million mapped reads, RPKM).
```{r, eval=FALSE}
# ge_18Q3 <- read.delim("./../htscreens_giant_files/CCLE_depMap_19Q1_TPM_20190305.csv.gz", skip = 2, header = TRUE, sep = "\t", check.names = FALSE)
# # Edit columns
# ge_18Q3$Name <- NULL
# colnames(ge_18Q3)[1] <- "Hugo_Symbol"
# # Melt
# ge_melt_18Q3 <- melt(data = ge_18Q3, id.vars = "Hugo_Symbol", measure.vars = colnames(ge_18Q3[2:ncol(ge_18Q3)]), value.name = "RPKM")
# ## Split variable column
# ge_melt_18Q3 <- with(ge_melt_18Q3, cbind(Hugo_Symbol, colsplit(variable, pattern = " ", names = c("CCLE_Name", "DepMap_ID")), RPKM))
# ## Remove parentheses around Broad IDs
# ge_melt_18Q3$DepMap_ID <- gsub("\\(|\\)", "", ge_melt_18Q3$DepMap_ID)
# saveRDS(ge_melt_18Q3, "./../htscreens_giant_files/ge_melt_18Q3.rds", compress = "xz")
```

@@

## G2P

```{r}
g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
g2p[, 1:2] <- NULL
g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)

g2p$Drug <- tolower(g2p$Drug)
g2p[g2p == -1] <- NA
g2p$Ref[g2p$Ref == "None"] <- NA
g2p$Alt[g2p$Alt == "None"] <- NA
g2p$Drug_Gene <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene), NA, paste0(g2p$Drug, "_", g2p$Gene))
g2p$Drug_Gene_Lin <- ifelse(is.na(g2p$Drug) | is.na(g2p$Gene) | is.na(g2p$group_general_lineage_name), NA, paste0(g2p$Drug, "_", g2p$Gene, "_", g2p$group_general_lineage_name))
g2p$position <- paste0("g.chr", g2p$Chromosome, ":", g2p$End, g2p$Ref, ">", g2p$Alt)
g2p$position <- ifelse(grepl("NA", g2p$position), NA, g2p$position)
g2p_filt <- subset(g2p, grepl("^CID", g2p$DrugID))

g2p_dgls <-  unique(g2p_filt$Drug_Gene_Lin[!is.na(g2p_filt$Drug_Gene_Lin)])
g2p_druggenes <- unique(g2p_filt$Drug_Gene[!is.na(g2p_filt$Drug_Gene)])
g2p_drugs <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[1]))
g2p_genes <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[2]))
g2p_lins <- unique(sapply(strsplit(g2p_dgls, "_", fixed = TRUE), function(x) x[3]))
g2p_druggenes
g2p_drugs
g2p_genes
g2p_lins

# Order and genes taken from pink heatmapo from Daniel's analyses
g2p_genes <- c("EGFR", "KRAS", "ERBB2", "ERBB3", "MET", "ALK", "ROS1", "PDGFRA", "ABL1", "KIT", "PDGFRB", "PDGFB", "BRAF", "G6PD", "RET", "BRCA1", "BRCA2", "UGT1A1", "TSC1", "TSC2", "AKT1", "IDH2", "DPYD", "ESR1", "CYP19A1", "TPMT", "FLT3", "NPM1", "DNMT3A", "PML", "PTCH1", "JAK2", "MYD88", "MGMT")
```

```{r}
# levels(g2p_filt$Phenotype.Description)
unique(g2p_filt$group_generals_lineage_name)
levels(g2p_filt$group_general_lineage_name)

g2p_nonCID <- subset(g2p, !grepl("^CID", g2p$DrugID))
summ <- g2p_nonCID %>% group_by(Drug, DrugID) %>% tally() %>% summarize(DrugID = DrugID, n = n, percent = formatC(n / 402 * 100, digits = 6, format = "f"))
summ
```

```{r, eval=FALSE}
cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
ge_melt_18Q3 <- readRDS("./../htscreens_giant_files/ge_melt_18Q3.rds")
# ge_melt_19Q1 <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")

# maf_filt_dan <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
# write.table(maf_filt_dan, file = "~/Desktop/maf_filt_dan_19Q1_2018112.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

## Drug screens

### Merge drug data and annotations

```{r}
maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
test <- filter(maf_df, Hugo_Symbol %in% g2p_genes) %>% count(Hugo_Symbol, CCLE_Name)
test <- test[order(test$n, decreasing = TRUE),]
```

`r nrow(filter(test, n == 1))`/`r nrow(test)` gene-cell line combinations have more than one mutation in the MAF file. This is corrected in the point mutation filtering done below.

```{r, eval=FALSE}
# Drug metadata
drug_meta <- read.delim("./data_munging/drug_id_drug_name_table_10_12_2018.tsv", sep = "\t", header = FALSE)
colnames(drug_meta) <- c("CID", "Drug")
drug_meta$Drug <- tolower(drug_meta$Drug)
maf_df_g2p <- filter(maf_df, Hugo_Symbol %in% g2p_genes)
ge_filt_18Q3 <- filter(ge_melt_18Q3, Hugo_Symbol %in% g2p_genes)
# ge_filt_19Q1 <- filter(ge_melt_19Q1, Hugo_Symbol %in% g2p_genes)
cn_filt <- filter(cn_melt, Hugo_Symbol %in% g2p_genes)

# CCLE
ccle <- read.delim("./data_munging/data_drug_auc_ccle_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ccle <- merge(drug_meta, ccle, by = "CID")
ccle_melt <- melt(ccle, id.vars = c("CID", "Drug"), measure.vars = colnames(ccle)[3:ncol(ccle)], variable.name = "accession_id", value.name = "ActArea")
ccle_grid <- expand.grid("accession_id" = unique(ccle_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ccle_data <- merge(ccle_grid, ccle_melt, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, ccl_converter, by = "accession_id", all.x = TRUE)
ccle_data <- merge(ccle_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
ccle_data$Mutation_Status_Nonsilent <- ifelse(is.na(ccle_data$Mutation_Status_Nonsilent), "Wildtype", ccle_data$Mutation_Status_Nonsilent)
ccle_data <- merge(ccle_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# ccle_data <- merge(ccle_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ccle_data <- merge(ccle_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ccle_data$Hugo_Symbol <- factor(ccle_data$Hugo_Symbol)
ccle_data$ActArea <- as.numeric(ccle_data$ActArea)
# CCLE AUC is actually AOC
# assuming scale is 0-8, transform to range between 0 and 1
# get AUC by 1 - AOC
ccle_data$AUC <- 1 - (ccle_data$ActArea / 8)
ccle_data <- filter(ccle_data, !is.na(ccle_data$AUC))
ccle_data$AUC_zscore <- (ccle_data$AUC - mean(ccle_data$AUC)) / sd(ccle_data$AUC)
ccle_data$Color_Nonsilent <- ifelse(ccle_data$Mutation_Status_Nonsilent == "Wildtype", "palegreen3", "springgreen4")
ccle_data$Color_Nonsilent <- factor(ccle_data$Color_Nonsilent)
ccle_data$Drug_Gene <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol)
ccle_data$Drug_Gene_Lin <- paste0(ccle_data$Drug, "_", ccle_data$Hugo_Symbol, "_", ccle_data$group_general_lineage_name)
saveRDS(ccle_data, "./data_munging/19Q1/ccle_data_19Q1_g2pgenes.rds", compress = "xz")

# CTRP
ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ctrp <- merge(drug_meta, ctrp, by = "CID")
ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = g2p_genes)
ctrp_data <- merge(ctrp_grid, ctrp_melt, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, ccl_converter, by = "accession_id", all.x = TRUE)
ctrp_data <- merge(ctrp_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
ctrp_data$Mutation_Status_Nonsilent <- ifelse(is.na(ctrp_data$Mutation_Status_Nonsilent), "Wildtype", ctrp_data$Mutation_Status_Nonsilent)
ctrp_data <- merge(ctrp_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# ctrp_data <- merge(ctrp_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ctrp_data <- merge(ctrp_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
ctrp_data$Hugo_Symbol <- factor(ctrp_data$Hugo_Symbol)
ctrp_data$AUC <- as.numeric(ctrp_data$AUC)
ctrp_data <- filter(ctrp_data, !is.na(ctrp_data$AUC))
ctrp_data$AUC_zscore <- (ctrp_data$AUC - mean(ctrp_data$AUC)) / sd(ctrp_data$AUC)
ctrp_data$Color_Nonsilent <- ifelse(ctrp_data$Mutation_Status_Nonsilent == "Wildtype", "slategray3", "steelblue4")
ctrp_data$Color_Nonsilent <- factor(ctrp_data$Color_Nonsilent)
ctrp_data$Drug_Gene <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol)
ctrp_data$Drug_Gene_Lin <- paste0(ctrp_data$Drug, "_", ctrp_data$Hugo_Symbol, "_", ctrp_data$group_general_lineage_name)
saveRDS(ctrp_data, "./data_munging/19Q1/ctrp_data_19Q1_g2pgenes.rds", compress = "xz")

# GDSC
gdsc <- read.delim("./data_munging/data_drug_auc_gdsc_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
gdsc <- merge(drug_meta, gdsc, by = "CID")
gdsc_melt <- melt(gdsc, id.vars = c("CID", "Drug"), measure.vars = colnames(gdsc)[3:ncol(gdsc)], variable.name = "accession_id", value.name = "AUC")
gdsc_grid <- expand.grid("accession_id" = unique(gdsc_melt$accession_id), "Hugo_Symbol" = g2p_genes)
gdsc_data <- merge(gdsc_grid, gdsc_melt, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, ccl_converter, by = "accession_id", all.x = TRUE)
gdsc_data <- merge(gdsc_data, maf_df_g2p, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
gdsc_data$Mutation_Status_Nonsilent <- ifelse(is.na(gdsc_data$Mutation_Status_Nonsilent), "Wildtype", gdsc_data$Mutation_Status_Nonsilent)
gdsc_data <- merge(gdsc_data, ge_filt_18Q3, by = c("Hugo_Symbol", "CCLE_Name", "DepMap_ID"), all.x = TRUE)
# gdsc_data <- merge(gdsc_data, ge_filt_19Q1, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
gdsc_data <- merge(gdsc_data, cn_filt, by = c("Hugo_Symbol", "DepMap_ID"), all.x = TRUE)
gdsc_data$Hugo_Symbol <- factor(gdsc_data$Hugo_Symbol)
gdsc_data$AUC <- as.numeric(gdsc_data$AUC)
gdsc_data <- filter(gdsc_data, !is.na(gdsc_data$AUC))
gdsc_data$AUC_zscore <- (gdsc_data$AUC - mean(gdsc_data$AUC)) / sd(gdsc_data$AUC)
gdsc_data$Color_Nonsilent <- ifelse(gdsc_data$Mutation_Status_Nonsilent == "Wildtype", "paleturquoise3", "turquoise4")
gdsc_data$Color_Nonsilent <- factor(gdsc_data$Color_Nonsilent)
gdsc_data$Drug_Gene <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol)
gdsc_data$Drug_Gene_Lin <- paste0(gdsc_data$Drug, "_", gdsc_data$Hugo_Symbol, "_", gdsc_data$group_general_lineage_name)
saveRDS(gdsc_data, "./data_munging/19Q1/gdsc_data_19Q1_g2pgenes.rds", compress = "xz")
```

### Filter drug data

```{r, eval=FALSE}
ccle_data <- readRDS("./data_munging/19Q1/ccle_data_19Q1_g2pgenes.rds")
ccle_data_ptmuts <- filter(ccle_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
ccle_data_ptmuts$Keep_PtMut_Tests <- ifelse(ccle_data_ptmuts$Reference_Allele == 1 | is.na(ccle_data_ptmuts$Reference_Allele), TRUE, ifelse(ccle_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
ccle_data_ptmuts <- filter(ccle_data_ptmuts, Keep_PtMut_Tests == TRUE)
# Remove columns that lead to duplicate mutation entries
ccle_data_ptmuts <- subset(ccle_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
ccle_data_ptmuts$Dataset <- "CCLE"
ccle_data_ptmuts$Hugo_Symbol <- ordered(ccle_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
ccle_data_ptmuts <- unique(ccle_data_ptmuts)
saveRDS(ccle_data_ptmuts, "./data_munging/19Q1/ccle_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")

ctrp_data <- readRDS("./data_munging/19Q1/ctrp_data_19Q1_g2pgenes.rds")
ctrp_data_ptmuts <- filter(ctrp_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
ctrp_data_ptmuts$Keep_PtMut_Tests <- ifelse(ctrp_data_ptmuts$Reference_Allele == 1 | is.na(ctrp_data_ptmuts$Reference_Allele), TRUE, ifelse(ctrp_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
ctrp_data_ptmuts <- filter(ctrp_data_ptmuts, Keep_PtMut_Tests == TRUE)
# Remove columns that lead to duplicate mutation entries
ctrp_data_ptmuts <- subset(ctrp_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
ctrp_data_ptmuts$Dataset <- "CTRP"
ctrp_data_ptmuts$Hugo_Symbol <- ordered(ctrp_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
ctrp_data_ptmuts <- unique(ctrp_data_ptmuts)
saveRDS(ctrp_data_ptmuts, "./data_munging/19Q1/ctrp_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")

gdsc_data <- readRDS("./data_munging/19Q1/gdsc_data_19Q1_g2pgenes.rds")
gdsc_data_ptmuts <- filter(gdsc_data, Reference_Allele == 1 | Reference_Allele == 0 | is.na(Reference_Allele))
gdsc_data_ptmuts$Keep_PtMut_Tests <- ifelse(gdsc_data_ptmuts$Reference_Allele == 1 | is.na(gdsc_data_ptmuts$Reference_Allele), TRUE, ifelse(gdsc_data_ptmuts$Tumor_Seq_Allele1 == 1, TRUE, FALSE))
gdsc_data_ptmuts <- filter(gdsc_data_ptmuts, Keep_PtMut_Tests == TRUE)
# Remove columns that lead to duplicate mutation entries
gdsc_data_ptmuts <- subset(gdsc_data_ptmuts, select = -c(Variant_Classification, Reference_Allele, Tumor_Seq_Allele1, Genome_Change, Keep_PtMut_Tests))
gdsc_data_ptmuts$Dataset <- "GDSC"
gdsc_data_ptmuts$Hugo_Symbol <- ordered(gdsc_data_ptmuts$Hugo_Symbol, levels = g2p_genes)
gdsc_data_ptmuts <- unique(gdsc_data_ptmuts)
saveRDS(gdsc_data_ptmuts, "./data_munging/19Q1/gdsc_data_19Q1_g2pgenes_ptmuts.rds", compress = "xz")
```

```{r}
ccle_data <- readRDS("./data_munging/19Q1/ccle_data_19Q1_g2pgenes.rds")
ctrp_data <- readRDS("./data_munging/19Q1/ctrp_data_19Q1_g2pgenes.rds")
gdsc_data <- readRDS("./data_munging/19Q1/gdsc_data_19Q1_g2pgenes.rds")
ccle_data_ptmuts <- readRDS("./data_munging/19Q1/ccle_data_19Q1_g2pgenes_ptmuts.rds")
ctrp_data_ptmuts <- readRDS("./data_munging/19Q1/ctrp_data_19Q1_g2pgenes_ptmuts.rds")
gdsc_data_ptmuts <- readRDS("./data_munging/19Q1/gdsc_data_19Q1_g2pgenes_ptmuts.rds")

# Filter drug screen datasets for G2P drug-gene associations
ccle_data_g2p <- filter(ccle_data_ptmuts, Drug_Gene %in% g2p_druggenes)
ccle_data_g2p$Mutation_Status_Nonsilent <- factor(ccle_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p <- filter(ctrp_data_ptmuts, Drug_Gene %in% g2p_druggenes)
ctrp_data_g2p$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p <- filter(gdsc_data_ptmuts, Drug_Gene %in% g2p_druggenes)
gdsc_data_g2p$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))

# Filter drug screen datasets for G2P drug-gene-lineage associations
ccle_data_g2p_dgl <- filter(ccle_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
ccle_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p_dgl <- filter(ctrp_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
ctrp_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p_dgl <- filter(gdsc_data_ptmuts, Drug_Gene_Lin %in% g2p_dgls)
gdsc_data_g2p_dgl$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_dgl$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))

# Filter drug screen datasets for G2P drugs and genes
ccle_data_g2p_grid <- filter(ccle_data_ptmuts, Drug %in% g2p_drugs)
ccle_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ccle_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
ctrp_data_g2p_grid <- filter(ctrp_data_ptmuts, Drug %in% g2p_drugs)
ctrp_data_g2p_grid$Mutation_Status_Nonsilent <- factor(ctrp_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))
gdsc_data_g2p_grid <- filter(gdsc_data_ptmuts, Drug %in% g2p_drugs)
gdsc_data_g2p_grid$Mutation_Status_Nonsilent <- factor(gdsc_data_g2p_grid$Mutation_Status_Nonsilent, levels = c("Mutant", "Wildtype"))

# Testing
test_ccle <- ccle_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
test_ctrp <- ctrp_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()
test_gdsc <- gdsc_data_ptmuts %>% group_by(Hugo_Symbol, Mutation_Status_Nonsilent) %>% tally()

# drug_summ <- data.frame(Drug = g2p_drugs, Dataset_Count = 0)
```

>>>>

```{r}
library(ggpubr)
library(ggrepel)
library(ggsignif)
library(kableExtra)
library(reshape2)
library(tidyverse)
library(naniar)
theme_set(theme_light())
```

@@

@@

## Denise's GCN dataframes

Code for Denise's graph convolutional networks analyses (see meeting notes from 6 March 2019).
- Convert drug/compound names to all capitalized for harmonization.

```{r, eval=TRUE}
maf_df <- readRDS("./data_munging/19Q1/maf_df_19Q1.rds")
cn_melt <- readRDS("./data_munging/19Q1/cn_melt_19Q1.rds")
ge_melt <- readRDS("./data_munging/19Q1/ge_melt_19Q1.rds")

ccle <- read.delim("./data_munging/pharmacogenomics_raw_files/CCLE_NP24.2009_Drug_data_2015.02.24_20190307.csv", sep = ",", header  = TRUE, check.names = FALSE)
ctrp <- read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.data.curves_post_qc.txt.gz", sep = "\t", header  = TRUE, check.names = FALSE)
gdsc <- read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_v17.3_fitted_dose_response_20190306.csv.gz", sep = ",", header  = TRUE, check.names = FALSE)

## CCLE
# Note that ActArea is NOT an AUC value
ccle_filt <- ccle[, c("CCLE Cell Line Name", "ActArea", "Compound")]
ccle_filt$source_ccl_name <- sapply(strsplit(as.character(ccle_filt$`CCLE Cell Line Name`), split = "_"), function(x) x[1])
ccle_filt$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccle_filt$`CCLE Cell Line Name`, ignore.case = TRUE))
ccle_filt$source_histology <- ifelse(as.character(ccle_filt$source_histology) == "", NA, as.character(ccle_filt$source_histology))
ccle_filt$compound_name <- toupper(ccle_filt$Compound)
colnames(ccle_filt)[colnames(ccle_filt) == "ActArea"] <- "AUC"
ccle4harm_long <- select(ccle_filt, source_ccl_name, source_histology, compound_name, AUC)
ccle4harm_long$source <- "CCLE"
ccle4harm_long$sample_id <- with(ccle4harm_long, paste(source, source_ccl_name, source_histology, sep = "_"))
ccle4harm <- dcast(ccle4harm_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
ccle4harm[, 5:ncol(ccle4harm)] <- ccle4harm[, 5:ncol(ccle4harm)] %>% replace_with_na_all(condition = ~.x == 10000)

## CTRP
# area_under_curve: integrated area under the sigmoid-fit concentration-response curve
ctrp_filt <- ctrp[, c("experiment_id", "area_under_curve", "master_cpd_id")]
ctrp_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_cell_line_20190306.txt"), master_ccl_id, ccl_name, ccle_primary_site)
ctrp_meta_exp <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_experiment_20190306.txt"), experiment_id, master_ccl_id)
ctrp_meta_cpd <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_compound_20190306.txt"), master_cpd_id, cpd_name)
ctrp_keep <- merge(merge(ctrp_meta_ccl, ctrp_meta_exp, by = "master_ccl_id", all = TRUE), merge(ctrp_meta_cpd, ctrp_filt, by = "master_cpd_id", all = TRUE), by = "experiment_id", all = TRUE)
ctrp_keep$cpd_name <- toupper(ctrp_keep$cpd_name)
ctrp_keep$ccle_primary_site <- ifelse(as.character(ctrp_keep$ccle_primary_site) == "", NA, as.character(ctrp_keep$ccle_primary_site))
ctrp4harm_long <- select(ctrp_keep, ccl_name, ccle_primary_site, cpd_name, area_under_curve)
colnames(ctrp4harm_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
ctrp4harm_long$source <- "CTRP"
ctrp4harm_long$sample_id <- with(ctrp4harm_long, paste(source, source_ccl_name, source_histology, sep = "_"))
ctrp4harm <- dcast(ctrp4harm_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
ctrp4harm[, 5:ncol(ctrp4harm)] <- ctrp4harm[, 5:ncol(ctrp4harm)] %>% replace_with_na_all(condition = ~.x == 10000)

## GDSC
gdsc_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_Cell_Lines_Details.csv", sep = ","), Line, Site)
gdsc_filt <- gdsc[, c("CELL_LINE_NAME", "DRUG_NAME", "AUC")]
gdsc_filt$DRUG_NAME <- toupper(gdsc_filt$DRUG_NAME)
colnames(gdsc_filt)[colnames(gdsc_filt) ==  "CELL_LINE_NAME"] <- "Line"
gdsc_filt <- merge(gdsc_filt, gdsc_meta_ccl, by = "Line", all = TRUE)
gdsc4harm_long <- select(gdsc_filt, Line, Site, DRUG_NAME, AUC)
colnames(gdsc4harm_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
gdsc4harm_long$source <- "GDSC"
gdsc4harm_long$sample_id <- with(gdsc4harm_long, paste(source, source_ccl_name, source_histology, sep = "_"))
gdsc4harm <- dcast(gdsc4harm_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
gdsc4harm[, 5:ncol(gdsc4harm)] <- gdsc4harm[, 5:ncol(gdsc4harm)] %>% replace_with_na_all(condition = ~.x == 10000)

## BIND ALL
pgx_harm_list <- list(ccle4harm, ctrp4harm, gdsc4harm)
pgx_harm_names <- unique(unlist(lapply(pgx_harm_list, names)))
pgx_harm <- do.call(rbind,
                    c(lapply(pgx_harm_list,
                             function(x) data.frame(c(x,
                                                      sapply(setdiff(pgx_harm_names, names(x)),
                                                             function(y) NA)
                                                      )
                                                    )
                             )
                      )
                    )
```
